raptr: Representative and Adequate Prioritization Toolkit in R

### 2016-11-23 code/rmarkdown/figures.Rmd
+ resize figures to journal specifications

@@

```{r, echo=FALSE, messages=FALSE, results='hide', fig.height=1.5, fig.width=4.5, fig.cap='Simulated distributions of three species. Squares denote planning units. The color of each planning unit indicates the probability that each species inhabits it. Panel (a) shows the uniformly distributed species, panel (b) shows the normally distributed species, and panel (c) shows the bimodally distributed species.'}
# prepare data
sim.pus.occ.FPLY <- ldply(
	seq_len(nrow(sim.species)),
	function(i) {
		curr.DF <- sim.pus.FPLY
		curr.DF$species <- sim.species$name[i]
		curr.DF$Probability <- sim.dps[[i]]@weights[as.numeric(curr.DF$id)]
		return(curr.DF)
	}
)
sim.pus.occ.FPLY$species <- gsub('\n', ' ', as.character(sim.pus.occ.FPLY$species))
sim.pus.occ.FPLY$species <- factor(as.character(sim.pus.occ.FPLY$species), levels=gsub('\n', ' ', sim.species$name)) 
# make letter data.frame
sim.pus.occ.letters.DF <- data.frame(
	x=gCentroid(sim.pus[1,])@coords[1],
	y=gCentroid(sim.pus[1,])@coords[2],
	species=unique(sim.pus.occ.FPLY$species),
	letter=paste0('(', letters[seq_along(sim.species$name)], ')')
)
# make plot
ggplot() +
	geom_polygon(data=sim.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Probability), color='black') +
	theme_classic() +
	geom_text(data=sim.pus.occ.letters.DF, aes(x=x, y=y, label=letter), size=2, color='white') +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 5, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(),
		legend.position=c(1.15, 0.6)) +
	facet_wrap(~ species, ncol=3)
```

```{r, echo=FALSE, fig.height=3.5, fig.width=5, fig.cap=paste0('Simulation study prioritizations. Each panel shows a prioritization generated for a single species using a set of parameters. Squares denote planning units, with dark green showing those planning units selected for protection in a particular prioritisation. The top row of panels (a, d, g, j) shows prioritizations generated for the uniformly distributed species, middle row of panels (b, e, h, k) for the normally distributed species, and the bottom row of panels (c, f, i, l) for the bimodally distributed species. Each column of panels corresponds to a different set of parameters used to generate the prioritisation. The left column of panels (a--c) shows prioritizations generated using only ',(sim.params.LST[[MODE]]$amount.target*100),' % amount targets, the middle-left column of panels (d--f) for prioritizations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount and ',(sim.params.LST[[MODE]]$space.target*100),' % space targets, the middle-right column of panels (g--i) for prioritizations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount based targets and a boundary length modifier (BLM) of ',sim.params.LST[[MODE]]$blm,', and the right column of panels (j--l) for prioritizations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount and ',(sim.params.LST[[MODE]]$space.target*100),' % space targets and also a boundary length modifier of ',(sim.params.LST[[MODE]]$blm),'.')}
# prepare data
sim.pus.sel.FPLY <- ldply(
	seq_len(nrow(sim.spp.DF)),
	function(i) {
		curr.DF <- sim.pus.FPLY %>% mutate(species=sim.spp.DF$species[i], prioritisation=sim.spp.DF$prioritisation[i])
		curr.selection <- selections(sim.prioritisations[[as.character(sim.spp.DF$species[i])]][[as.character(sim.spp.DF$prioritisation[i])]])[as.numeric(curr.DF$id)]
		curr.DF$Selection <-  c('discarded','selected')[curr.selection+1]
		return(curr.DF)
	}
)
sim.pus.sel.FPLY$prioritisation <- factor(as.character(sim.pus.sel.FPLY$prioritisation),
	levels=c('Amount\ntargets', 'Amount &\nspace targets', 'Amount target\nand BLM', 'Amount & space\ntargets and BLM'))
# prepare plotting data
sim.letter.DF2 <- mutate(sim.spp.DF, letter=paste0('(', letters[seq_along(species)],')'))
sim.letter.DF2$long <- gCentroid(sim.pus[1,])@coords[1]
sim.letter.DF2$lat <- gCentroid(sim.pus[1,])@coords[2]
# make plot
ggplot() +
	geom_polygon(data=sim.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Selection), color='black') +
	geom_text(data=sim.letter.DF2, aes(label=letter, x=long, y=lat), color='black', size=1.8) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.ticks.x=element_blank(), axis.ticks.y=element_blank(),
		axis.text=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(),
		axis.line=element_blank(), axis.line.x=element_blank(), axis.line.y=element_blank(),
		plot.background=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		panel.background=element_blank(), panel.border=element_blank(), legend.position='none',
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank()) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	facet_grid(species ~ prioritisation)
```

```{r, echo=FALSE, fig.height=2.5, fig.width=3, fig.cap='Distribution of environmental variation across Queensland, Australia. Squares denote planning units. The panels show the first and second main gradients of climatic variation.'}
# prepare data
cs1.pca.FPTS <- ldply(
	seq_len(cs1.params.LST[[MODE]]$n.pc.layers),
	function(i) {
		curr.DF <- cs1.bioclim.RAST[[i]] %>% 
			aggregate(10) %>% 
			rasterToPoints() %>% 
			as.data.frame()
		names(curr.DF)[3] <- 'Score'
		curr.DF$pc <- paste0('Principal component ',i)
		return(curr.DF)
	}
)
# make plots
p1 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[1]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
	) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ pc)
p2 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[2]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
		) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ pc)
# render plots
grid.arrange(p1, p2, ncol=2)
```

```{r, echo=FALSE, fig.height=4.5, fig.width=4.0, fig.cap='Distribution of the species used in the first case-study. Squares denote planning units. Each panel shows the distribution of a different species.'}
# prepare data
cs1.pus.occ.FPLY <- ldply(
	seq_along(cs1.params.LST[[MODE]]$common.names),
	function(i) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$species <- cs1.params.LST[[MODE]]$common.names[i]
		curr.DF$Occupancy <- 'absent'
		curr.DF$Occupancy[which(curr.DF$id %in% filter(cs1.ru@data@pu.species.probabilities, species==i)$pu)] <- 'present'
		return(curr.DF)
	}
)
cs1.pus.occ.FPLY$species <- factor(as.character(cs1.pus.occ.FPLY$species), levels=cs1.params.LST[[MODE]]$common.names)
# make letter data.frame
cs1.pus.occ.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.05)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.965)),
	species=unique(cs1.pus.occ.FPLY$species),
	letter=paste0('(', letters[seq_along(unique(cs1.pus.occ.FPLY$species))], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), color='black') +
	geom_text(data=cs1.pus.occ.letters.DF, aes(x=x, y=y, label=letter), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.045, 1.035), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ species, ncol=2)
```

```{r, echo=FALSE, fig.height=2.5, fig.width=4.5, fig.cap=paste0('Prioritizations for the niche-based case-study in Queensland, Australia. Squares represent planning units. Dark green planning units for selected for protection and pale green units were discarded. Panel (a) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets. Panel (b) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets and ',cs1.params.LST[[MODE]]$space.target*100,' % niche targets')}
# prepare data
cs1.pus.sel.FPLY <- ldply(
	names(cs1.prioritisations),
	function(x) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$Prioritisation <- x
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.DF$id %in% which(as.logical(selections(cs1.prioritisations[[x]])))] <- 'selected'
		return(curr.DF)
	}
)
cs1.pus.sel.FPLY$Prioritisation <- factor(as.character(cs1.pus.sel.FPLY$Prioritisation), levels=names(cs1.prioritisations))
# make letter data.frame
cs1.pus.sel.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.05)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.965)),
	Prioritisation=names(cs1.prioritisations),
	letter=paste0('(', letters[1:2], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Solution), color='black') +
	geom_text(data=cs1.pus.sel.letters.DF, aes(x=x, y=y, label=letter), color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.03, 1.03), legend.justification=c(1,1), legend.key.size=unit(3, 'mm')
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ Prioritisation, ncol=2)
```

```{r, echo=FALSE, fig.height=4.5, fig.width=4.5, fig.cap=paste0('Study area and data used in the second case-study. Squares denote planning units. Panel (a) shows all grid cells surveyed by the IntraBioDiv project. Grid cells occupied by ',tolower(cs2.params.LST[[MODE]]$common.name),' are shown in bright blue. The subsequent panels contain only the grid cells that were occupied by the species. Panel (b) shows the opportunity cost of each planning unit (estimated as the total human population density). Panels (c--d) show the spatial distribution of the ordinated genetic data. These values describe the typical genetic characteristics of individuals in each planning unit. Planning units with similar values/colors contain individuals with similar loci polymorphisms.')}
# prepare full grid data
cs2.spp.grid.FPLY <- cs2.grid.FPLY
cs2.spp.grid.FPLY$Title <- 'Occupancy'
cs2.spp.grid.FPLY$Occupancy <- 'absent'
cs2.spp.grid.FPLY$Occupancy[which(cs2.grid.PLY@data[[cs2.params.LST[[MODE]]$species.name]][as.numeric(cs2.spp.grid.FPLY$id)]==1)] <- 'present'

cs2.spp.grid.letters.DF <- data.frame(
	x=unname(cs2.grid.PLY@bbox[1,1] + (diff(cs2.grid.PLY@bbox[1,])*0.05)),
	y=unname(cs2.grid.PLY@bbox[2,1] + (diff(cs2.grid.PLY@bbox[2,])*0.95)),
	letter=('(a)')
)

@@

cs2.spp.grid.sub.letters.DF <- data.frame(
	x=unname(cs2.grid.sub.PLY@bbox[1,1] + (diff(cs2.grid.sub.PLY@bbox[1,])*0.05)),
	y=unname(cs2.grid.sub.PLY@bbox[2,1] + (diff(cs2.grid.sub.PLY@bbox[2,])*0.95)),
	letter=c('(b)','(c)','(d)')
)

>>>>

column.width <- 2.75591

@@

```{r, echo=FALSE, messages=FALSE, results='hide', fig.height=1.6, fig.width=column.width, fig.cap='Simulated distributions of three species. Squares denote planning units. The color of each planning unit indicates the probability that each species inhabits it. Panel (a) shows the uniformly distributed species, panel (b) shows the normally distributed species, and panel (c) shows the bimodally distributed species.'}
# prepare data
sim.pus.occ.FPLY <- ldply(
	seq_len(nrow(sim.species)),
	function(i) {
		curr.DF <- sim.pus.FPLY
		curr.DF$species <- sim.species$name[i]
		curr.DF$Probability <- sim.dps[[i]]@weights[as.numeric(curr.DF$id)]
		return(curr.DF)
	}
)
sim.pus.occ.FPLY$species <- gsub('\n', ' ', as.character(sim.pus.occ.FPLY$species))
sim.pus.occ.FPLY$species <- factor(as.character(sim.pus.occ.FPLY$species), levels=gsub('\n', ' ', sim.species$name)) 
# make letter data.frame
sim.pus.occ.letters.DF <- data.frame(
	x=min(sim.pus.occ.FPLY$long) + 1.5,
	y=max(sim.pus.occ.FPLY$lat) - 1.5,
	species=unique(sim.pus.occ.FPLY$species),
	letter=paste0('(', letters[seq_along(sim.species$name)], ')')
)
# make plot
ggplot() +
	geom_polygon(data=sim.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Probability), color='black') +
	theme_classic() +
	geom_label(data=sim.pus.occ.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=2) +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=7),
    axis.title = element_blank(),
    legend.title = element_text(color='black', size=7),
		legend.text = element_text(color='black', size=7),
		legend.margin = unit(0, 'cm'),
		legend.position='bottom') +
	facet_wrap(~ species, ncol=3)
```

```{r, echo=FALSE, fig.height=3.5, fig.width=2*column.width, fig.cap=paste0('Simulation study prioritizations. Each panel shows a prioritization generated for a single species using a set of parameters. Squares denote planning units, with dark green showing those planning units selected for protection in a particular prioritisation. The top row of panels (a, d, g, j) shows prioritizations generated for the uniformly distributed species, middle row of panels (b, e, h, k) for the normally distributed species, and the bottom row of panels (c, f, i, l) for the bimodally distributed species. Each column of panels corresponds to a different set of parameters used to generate the prioritisation. The left column of panels (a--c) shows prioritizations generated using only ',(sim.params.LST[[MODE]]$amount.target*100),' % amount targets, the middle-left column of panels (d--f) for prioritizations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount and ',(sim.params.LST[[MODE]]$space.target*100),' % space targets, the middle-right column of panels (g--i) for prioritizations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount based targets and a boundary length modifier (BLM) of ',sim.params.LST[[MODE]]$blm,', and the right column of panels (j--l) for prioritizations generated using ',(sim.params.LST[[MODE]]$amount.target*100),' % amount and ',(sim.params.LST[[MODE]]$space.target*100),' % space targets and also a boundary length modifier of ',(sim.params.LST[[MODE]]$blm),'.')}
# prepare data
sim.pus.sel.FPLY <- ldply(
	seq_len(nrow(sim.spp.DF)),
	function(i) {
		curr.DF <- sim.pus.FPLY %>% mutate(species=sim.spp.DF$species[i], prioritisation=sim.spp.DF$prioritisation[i])
		curr.selection <- selections(sim.prioritisations[[as.character(sim.spp.DF$species[i])]][[as.character(sim.spp.DF$prioritisation[i])]])[as.numeric(curr.DF$id)]
		curr.DF$Selection <-  c('discarded','selected')[curr.selection+1]
		return(curr.DF)
	}
)
sim.pus.sel.FPLY$prioritisation <- factor(as.character(sim.pus.sel.FPLY$prioritisation),
	levels=c('Amount\ntargets', 'Amount &\nspace targets', 'Amount target\nand BLM', 'Amount & space\ntargets and BLM'))
# prepare plotting data
sim.letter.DF2 <- sim.spp.DF %>%
  mutate(letter=paste0('(', letters[seq_along(species)],')'),
         long=min(sim.pus.sel.FPLY$long) + 1.6,
         lat=max(sim.pus.sel.FPLY$lat) - 1.5)
# make plot
ggplot() +
	geom_polygon(data=sim.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Selection), color='black') +
	geom_label(data=sim.letter.DF2, aes(label=letter, x=long, y=lat), color='black', fill=alpha('white', 0.8), size=5) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.ticks.x=element_blank(), axis.ticks.y=element_blank(),
		axis.text=element_blank(), axis.text.x=element_blank(), axis.text.y=element_blank(),
		axis.line=element_blank(), axis.line.x=element_blank(), axis.line.y=element_blank(),
		plot.background=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		panel.background=element_blank(), panel.border=element_blank(), legend.position='none',
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank()) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	facet_grid(species ~ prioritisation)
```

```{r, echo=FALSE, fig.height=1.6, fig.width=column.width, fig.cap='Distribution of environmental variation across Queensland, Australia. Squares denote planning units. The panels show the first and second main gradients of climatic variation.'}
# prepare data
cs1.pca.FPTS <- ldply(
	seq_len(cs1.params.LST[[MODE]]$n.pc.layers),
	function(i) {
		curr.DF <- cs1.bioclim.RAST[[i]] %>% 
			aggregate(10) %>% 
			rasterToPoints() %>% 
			as.data.frame()
		names(curr.DF)[3] <- 'Score'
		curr.DF$pc <- paste0('PC ',i)
		return(curr.DF)
	}
)
# make plots
p1 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[1]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.height=unit(1.5, 'mm'), legend.key.width=unit(2, 'mm')
	) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	scale_fill_continuous(breaks=pretty(filter(cs1.pca.FPTS, pc==unique(pc)[1])$Score, n=3, min.n=2)) +
	facet_wrap(~ pc)
p2 <- ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_raster(data=filter(cs1.pca.FPTS, pc==unique(pc)[2]), aes(x=x, y=y, fill=Score)) +
	geom_polygon(data=cs1.pus.FPLY, aes(x=long, y=lat, group=group), fill=NA, color='black') +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='transparent', fill='transparent'),
		legend.position=c(1.1, 1.07), legend.justification=c(1,1), legend.key.height=unit(1.5, 'mm'), legend.key.width=unit(2, 'mm')
		) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	scale_fill_continuous(breaks=pretty(filter(cs1.pca.FPTS, pc==unique(pc)[2])$Score, n=2, min.n=2)) +
	facet_wrap(~ pc)
# render plots
grid.arrange(p1, p2, ncol=2)
```

```{r, echo=FALSE, fig.height=2.35, fig.width=column.width, fig.cap='Distribution of the species used in the first case-study. Squares denote planning units. Each panel shows the distribution of a different species. Planning units occupied by a species are shown in bright blue.'}
# prepare data
cs1.pus.occ.FPLY <- ldply(
	seq_along(cs1.params.LST[[MODE]]$common.names),
	function(i) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$species <- cs1.params.LST[[MODE]]$common.names[i]
		curr.DF$Occupancy <- 'absent'
		curr.DF$Occupancy[which(curr.DF$id %in% filter(cs1.ru@data@pu.species.probabilities, species==i)$pu)] <- 'present'
		return(curr.DF)
	}
)
cs1.pus.occ.FPLY$species <- factor(as.character(cs1.pus.occ.FPLY$species), levels=cs1.params.LST[[MODE]]$common.names)
# make letter data.frame
cs1.pus.occ.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.06)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.90)),
	species=unique(cs1.pus.occ.FPLY$species),
	letter=paste0('(', letters[seq_along(unique(cs1.pus.occ.FPLY$species))], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.occ.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), color='black', size=0.05) +
	geom_label(data=cs1.pus.occ.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=8),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ species, ncol=2)
```

```{r, echo=FALSE, fig.height=1.175, fig.width=column.width, fig.cap=paste0('Prioritizations for the niche-based case-study in Queensland, Australia. Squares represent planning units. Dark green planning units for selected for protection and pale green units were discarded. Panel (a) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets. Panel (b) shows the planning units selected when using ',cs1.params.LST[[MODE]]$amount.target*100,' % amount targets and ',cs1.params.LST[[MODE]]$space.target*100,' % niche targets')}
# prepare data
cs1.pus.sel.FPLY <- ldply(
	names(cs1.prioritisations),
	function(x) {
		curr.DF <- cs1.pus.FPLY
		curr.DF$Prioritisation <- x
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.DF$id %in% which(as.logical(selections(cs1.prioritisations[[x]])))] <- 'selected'
		return(curr.DF)
	}
)
cs1.pus.sel.FPLY$Prioritisation <- factor(as.character(cs1.pus.sel.FPLY$Prioritisation), levels=names(cs1.prioritisations))
# make letter data.frame
cs1.pus.sel.letters.DF <- data.frame(
	x=unname(cs1.pus@bbox[1,1] + (diff(cs1.pus@bbox[1,])*0.06)),
	y=unname(cs1.pus@bbox[2,1] + (diff(cs1.pus@bbox[2,])*0.90)),
	Prioritisation=names(cs1.prioritisations),
	letter=paste0('(', letters[1:2], ')')
)
# make plots
ggplot() +
	geom_polygon(data=aus.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs1.pus.sel.FPLY, aes(x=long, y=lat, group=group, fill=Solution), color='black', size=0.1) +
	geom_label(data=cs1.pus.sel.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', size=8),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Solution', values=c('discarded'='#f7fcfd', 'selected'='#00441b')) +
	coord_cartesian(xlim=cs1.pus@bbox[1,], ylim=cs1.pus@bbox[2,]) +
	facet_wrap(~ Prioritisation, ncol=2)
```

```{r, echo=FALSE, fig.height=2.5, fig.width=column.width, fig.cap=paste0('Study area and data used in the second case-study. Squares denote planning units. Panel (a) shows all grid cells surveyed by the IntraBioDiv project. Grid cells occupied by ',tolower(cs2.params.LST[[MODE]]$common.name),' are shown in bright blue. The subsequent panels contain only the grid cells that were occupied by the species. Panel (b) shows the opportunity cost of each planning unit (estimated as the total human population density). Panels (c--d) show the spatial distribution of the ordinated genetic data. These values describe the typical genetic characteristics of individuals in each planning unit. Planning units with similar values/colors contain individuals with similar loci polymorphisms.')}
# prepare full grid data
cs2.spp.grid.FPLY <- cs2.grid.FPLY
cs2.spp.grid.FPLY$Title <- 'Occupancy'
cs2.spp.grid.FPLY$Occupancy <- 'absent'
cs2.spp.grid.FPLY$Occupancy[which(cs2.grid.PLY@data[[cs2.params.LST[[MODE]]$species.name]][as.numeric(cs2.spp.grid.FPLY$id)]==1)] <- 'present'

cs2.spp.grid.letters.DF <- data.frame(
	x=unname(cs2.grid.PLY@bbox[1,1] + (diff(cs2.grid.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.PLY@bbox[2,1] + (diff(cs2.grid.PLY@bbox[2,])*0.90)),
	letter=('(a)')
)

@@

cs2.spp.grid.sub.letters.DF <- data.frame(
	x=unname(cs2.grid.sub.PLY@bbox[1,1] + (diff(cs2.grid.sub.PLY@bbox[1,])*0.06)),
	y=unname(cs2.grid.sub.PLY@bbox[2,1] + (diff(cs2.grid.sub.PLY@bbox[2,])*0.90)),
	letter=c('(b)','(c)','(d)')
)

# plot species data
p1 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.FPLY, aes(x=long, y=lat, group=group, fill=Occupancy), alpha=0.8, color='grey10') +
	geom_label(data=cs2.spp.grid.letters.DF, aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.position='none'
	) +
	scale_fill_manual(name='Occupancy', values=c('absent'='#132B43', 'present'='#56B1F7')) +
	coord_cartesian(xlim=buffered.range(cs2.grid.FPLY$long, 0), ylim=buffered.range(cs2.grid.FPLY$lat, 0)) +
	facet_wrap(~ Title)
# plot cost data
p2 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group), fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=Cost), alpha=0.8, color='grey10') +
	geom_label(data=cs2.spp.grid.sub.letters.DF[1,], aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
		axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
		legend.position=c(0.25, 0.55), legend.key.height=unit(2.5, 'mm'), legend.key.width=unit(3.25, 'mm'),
		legend.title=element_blank(), legend.direction='horizontal', legend.justification=c(0,1), legend.background=element_rect(size=unit(0.25, 'mm'))
	) +
	coord_cartesian(xlim=buffered.range(cs2.grid.sub.FPLY$long, 0), ylim=buffered.range(cs2.grid.sub.FPLY$lat, 0)) +
	scale_fill_continuous(name=element_blank(), breaks=pretty(cs2.spp.grid.sub.FPLY$Cost, n=3, min.n=2)) +
	facet_wrap(~ Title1)
# plot nmds axis 1
p3 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=nmds1), alpha=0.8, color='grey10') +
	geom_label(data=cs2.spp.grid.sub.letters.DF[2,], aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
    axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
    legend.position=c(0.25, 0.55), legend.key.height=unit(2.5, 'mm'), legend.key.width=unit(3.25, 'mm'),
    legend.title=element_blank(), legend.direction='horizontal', legend.justification=c(0,1), legend.background=element_rect(size=unit(0.25, 'mm'))
	) + 
	coord_cartesian(xlim=buffered.range(cs2.grid.sub.FPLY$long, 0), ylim=buffered.range(cs2.grid.sub.FPLY$lat, 0)) +
	scale_fill_gradient2(name=element_blank(), low='darkblue', mid='white', high='darkred', breaks=c(0, 0.3)) +
	facet_wrap(~ Title2)
# plot nmds axis 2
p4 <- ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),fill='grey85', color='grey70') +
	geom_polygon(data=cs2.spp.grid.sub.FPLY, aes(x=long, y=lat, group=group, fill=nmds2), alpha=0.8, color='grey10') +
	geom_label(data=cs2.spp.grid.sub.letters.DF[3,], aes(label=letter, x=x, y=y), color='black', fill=alpha('white', 0.8), size=3) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white'),
    axis.title=element_blank(), legend.background=element_rect(color='black', fill='white'),
